---
title: "John Franchak"
subtitle: "Curriculum Vitae"
execute:
  echo: false
  warning: false
format:
  html:
    toc-location: left
    email-obfuscation: javascript
  pdf: 
    fontfamily: tgpagella
    fontenc: T1
    colorlinks: false
    include-in-header: 
      text: |
        \usepackage{array,colortbl}
        \arrayrulecolor{white}
---
| Department of Psychology, University of California, Riverside  
| 900 University Avenue, Riverside, CA 92521

::: {.content-visible when-format="pdf"}
| email: [franchak@ucr.edu](mailto:franchak@ucr.edu)
| web: [padlab.ucr.edu](padlab.ucr.edu)
:::
::: {.content-visible when-format="html"}
{{< fa envelope title="Email" >}}  [franchak@ucr.edu](mailto:franchak@ucr.edu) 
{{< fa file-pdf title="Download" >}} [Download CV]("https://padlab.ucr.edu/Franchak_cv.pdf")
:::

# Employment and Education

 | 
|--|--------|
| 2022- | Associate Professor, Dept. of Psychology, **University of California, Riverside** |
| 2014-2022 | Assistant Professor, Dept. of Psychology, **University of California, Riverside** |
| 2013-2014 | Post-Doctoral Fellow, Dept. of Psychological and Brain Sciences, **Indiana University** (Sponsors: Chen Yu & Linda Smith) |
| 2011-2013 | Post-Doctoral Researcher, Dept. of Psychology, **New York University** (Sponsors: Karen Adolph & David Heeger)|
| 2009-2011 | Ph.D., Experimental Psychology, **New York University** (Advisor: Karen Adolph)|
| 2006-2009| M.A., Experimental Psychology, **New York University** |
| 2005-2006| Lab Coordinator, Dept. of Psychology, **Rutgers University, Newark** |
| 2001-2005| B.A., Cognitive Science, **University of Virginia** |
: {tbl-colwidths="[15,85]"}

# Research Interests
- Perceptual-motor development (posture, locomotion, reaching)
- Visual exploration in infants', children's, and adults' everyday behaviors
- Development of visual attention while viewing complex, dynamic media
- Motor learning and control (affordances, visual guidance of walking and reaching) 
- Ambulatory assessment (mobile eye tracking, accelerometry, ecological momentary assessment)

# Honors and Awards
| | |
|-|--------|
| 2020		| Visiting Scholar, **McPherson Eye Research Institute, University of Wisconsin-Madison** |
| 2015		| Rising Star, **Association for Psychological Science** |
| 2014		| Intel Best Paper Award *This hand is my hand: A probabilistic approach to hand disambiguation in egocentric video*, **IEEE Computer Vision and Pattern Recognition** |
| 2013		| Postdoctoral Fellowship, NICHD Training Grant, 5T32HD7475-17, *Training Program in Integrative Developmental Process*, **Indiana University** |
| 2012		| Best Methodological Paper *Understanding the development of motion processing by characterizing optic flow experienced by infants and their mothers*, **International Conference on Learning and Development** |
| 2011		| Martin Braine Dissertation Award, **New York University** |
| 2010		| Best Paper Award *Head-mounted eye-tracking of infants’ natural interactions:  A new method*, **ACM Eye Tracking Research & Applications** |
| 2009		| Sandra G. Wiener Student Investigator Award, **International Society for Developmental Psychobiology** |
: {tbl-colwidths="[5,95]"}

# Grant Support

### Extramural

 | 
|--|--------|
| 2022-2025 | James S. McDonnell Foundation Opportunity Award: *Characterizing infants' everyday motor and object experiences through computer vision analysis of caregiver-captured video surveys.* **John Franchak, PI, $250,000 3-year project.** |
| 2020-2024 | NSF BCS-1941449: *Developmental cascades: How motor development alters everyday learning*. **John Franchak, PI, $754,957 4-year total.** |
| 2018-2023	| NICHD R01-HD-094830: *PLAY (Play and Learning Across a Year)*. Karen Adolph, PI, $6,341,419 total award. **John Franchak, sub-award PI, $18,527 5-year total.** |
| 2018-2022	| NSF IIS-1763966: *CHS: Medium: Collaborative research: Designing virtual worlds for children - A developmental study of how children act, perceive, and reason spatially*. Robert Bodenheimer, PI, $539,504 total award. **John Franchak, consultant, $24,000 4-year total.** |	
| 2018-2021	| NSF BCS-1749594: *Picture book reading: Investigating a key source of linguistic input for early language development*. Jessica Montag, PI, $427,933 total award. **John Franchak, consultant, $5000 3-year total.** |
| 2018-2023	| NICHD R01-HD-033486: *Flexibility of learning in infant skill acquisition*, Karen Adolph, PI, total award $3,086,397. **John Franchak, consultant, $25,000 5-year total.** |
: {tbl-colwidths="[15,85]"}

### Intramural

 | 
|--|--------|
| Pending | UCR Center for Health Disparities Research FIRST Pilot Grant: *Sociocultural and emotion regulation processes that contextualize health disparities in Latinx children's anxiety*. Elizabeth Davis, PI, $50,000 total award. **John Franchak, co-PI**. |
|2021-2022 | UCR Exploration Center for Innovative Teaching & Engagement: Remote Course Conversion Grant. **John Franchak, PI, $8,000 1-year total**. |
|2021-2022 | UCR Center for Health Disparities Research Interdisciplinary Research Working Group Award: *Contextualizing Latinx children’s developing psychopathology: An interdisciplinary investigation of sociocultural and psychological processes contributing to health disparities in anxiety*. Elizabeth Davis, PI $2,500 total award. **John Franchak, co-PI**. |
| 2019-2021	| UCR Regents Faculty Development Fellowship: *Characterizing everyday opportunities for learning in the second year of life*. **John Franchak, PI, $5,000 2-year total**. |
| 2015-2017	| UCR Regents Faculty Fellowship: *Developmental changes in visual experiences over the first year of life*. **John Franchak, PI, $6,000 2-year award total**. |
: {tbl-colwidths="[15,85]"}

# Research 
\renewcommand{\arraystretch}{1.5}

```{r}
#|output: false
#|echo: false
library(tidyverse)
library(knitr)
refs <- read_csv("publications/publications.csv") %>% 
  mutate(authors = str_replace(authors, "Franchak, J.M.", "**Franchak, J.M.**")) 
```
### Manuscripts Invited/Under Review/In Revision
```{r}
refs  %>%  
  filter(type %in% c("Prep")) %>% 
  mutate(citation = sprintf("%s (under review). %s", authors, title)) %>% 
  select(citation) %>% 
  kable(col.names = "") 
```

### Peer-Reviewed Publications
::: {.content-visible when-format="pdf"}
```{r}
refs %>% filter(type %in% c("Journal","Proceedings")) %>% 
  mutate(numbers = str_c(", ", numbers)) %>% 
  mutate(numbers = replace_na(numbers, "")) %>% 
  mutate(citation = sprintf("%d.  %s (%d). [%s](https://padlab.ucr.edu/publications/%s) *%s*%s", row_number(), authors, year, title, url, venue, numbers)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
refs %>% filter(type %in% c("Journal","Proceedings")) %>% 
  mutate(numbers = str_c(", ", numbers)) %>% 
  mutate(numbers = replace_na(numbers, "")) %>% 
  mutate(citation = sprintf("[{{< fa file-pdf >}}](https://padlab.ucr.edu/publications/%s)  %s (%d). %s *%s*%s", url, authors, year, title, venue, numbers)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::

### Book Chapters
::: {.content-visible when-format="pdf"}
```{r}
refs %>% filter(type %in% c("Chapter")) %>% 
  mutate(numbers = str_c(", ", numbers)) %>% 
  mutate(numbers = replace_na(numbers, "")) %>% 
  mutate(citation = sprintf("%d.  %s (%d). [%s](https://padlab.ucr.edu/publications/%s) *%s*%s", row_number(), authors, year, title, url, venue, numbers)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
refs %>% filter(type %in% c("Chapter")) %>% 
  mutate(numbers = str_c(", ", numbers)) %>% 
  mutate(numbers = replace_na(numbers, "")) %>% 
  mutate(citation = sprintf("[{{< fa file-pdf >}}](https://padlab.ucr.edu/publications/%s) %s (%d). %s *%s*%s", url, authors, year, title, venue, numbers)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::

### Shared Datasets
<!-- GET LINKS WORKING HERE -->
```{r}
read_csv("publications/datasets.csv") %>% 
  mutate(citation = sprintf("%d. (%d) *%s* %s. ```doi:%s```", row_number(), year, title, venue, doi)) %>% 
  select(citation) %>% kable(col.names = "")
```
# Open Source Research and Teaching Materials

- *Eye Tracking Accuracy Calculator*, [https://github.com/JohnFranchak/et_accuracy](https://github.com/JohnFranchak/et_accuracy)
- *Dynamic ROI Coder for Matlab*, [https://github.com/JohnFranchak/roi_coder](https://github.com/JohnFranchak/roi_coder)
- *Principles of Data Science Course*, [https://github.com/psych-259-data-science-2022](https://github.com/psych-259-data-science-2022)
- *ICIS Head-Mounted Eye Tracking Workshop*, [https://github.com/ICIS-HMET-Workshop](https://github.com/ICIS-HMET-Workshop)
- *Matlab Utilities for Eye Tracking*, [https://github.com/JohnFranchak/et_tools](https://github.com/JohnFranchak/et_tools)
- *Escalator Psychophysical Toolbox*, [https://github.com/JohnFranchak/escalator_toolbox](https://github.com/JohnFranchak/escalator_toolbox)

# Presentations

### Conference Organizing

### Conference Papers

### Conference Posters

### Invited Colloquia

# Media Coverage