---
title: "John Franchak"
subtitle: "Curriculum Vitae"
execute:
  echo: false
  warning: false
format:
  html:
    toc-location: left
    email-obfuscation: javascript
  pdf: 
    fontfamily: tgpagella
    fontenc: T1
    colorlinks: false
    include-in-header: 
      text: |
        \usepackage{array,colortbl}
        \arrayrulecolor{white}
        \usepackage{fancyhdr}
        \pagestyle{fancy}
        \fancyhead{}
        \fancyhead[LO,LE]{\textbf{Franchak CV}}
        \fancyhead[RO,RE]{\thepage}
        \fancyfoot{}
---
```{r}
library(tidyverse)
library(lubridate)
library(knitr)
```
| Department of Psychology
| University of California, Riverside  
| 900 University Avenue, Riverside, CA 92521

::: {.content-visible when-format="pdf"}
| email: [franchak@ucr.edu](mailto:franchak@ucr.edu)
| web: [padlab.ucr.edu](https://padlab.ucr.edu)
:::
::: {.content-visible when-format="html"}
| {{< fa envelope title="Email" >}}  [franchak@ucr.edu](mailto:franchak@ucr.edu)
| {{< fa file-pdf title="Download" >}} [Download CV](https://padlab.ucr.edu/Franchak_cv.pdf) 
| {{< fa file-pdf title="Download" >}} [Download Research Statement](https://padlab.ucr.edu/Franchak_Research.pdf) 
:::

Last updated: `r sprintf("%s %d, %d", as.character(month(today(), label = T, abbr = F)), mday(today()), year(today()))`
\thispagestyle{empty}

# Employment and Education

 | 
|--|--------|
| 2022- | Associate Professor, Dept. of Psychology, **University of California, Riverside** |
| 2014-2022 | Assistant Professor, Dept. of Psychology, **University of California, Riverside** |
| 2013-2014 | Post-Doctoral Fellow, Dept. of Psychological and Brain Sciences, **Indiana University** (Sponsors: Chen Yu & Linda Smith) |
| 2011-2013 | Post-Doctoral Researcher, Dept. of Psychology, **New York University** (Sponsors: Karen Adolph & David Heeger)|
| 2009-2011 | Ph.D., Experimental Psychology, **New York University** (Advisor: Karen Adolph)|
| 2006-2009| M.A., Experimental Psychology, **New York University** |
| 2005-2006| Lab Coordinator, Dept. of Psychology, **Rutgers University, Newark** |
| 2001-2005| B.A., Cognitive Science, **University of Virginia** |
: {tbl-colwidths="[15,85]"}

# Research Interests
- Perceptual-motor development (posture, locomotion, reaching)
- Wearable sensing of infants' everyday physical activity using machine learning
- Ecological momentary assessment of infants' daily activities via caregiver smartphone surveys and video recordings
- Development of visual attention using mobile eye tracking and screen-based eye tracking
- Motor learning and control (affordances, visual guidance of walking and reaching)

# Honors and Awards
| | |
|-|--------|
| 2023		| Faculty of the Year, **Psychology Department, University of California, Riverside** |
| 2020		| Visiting Scholar, **McPherson Eye Research Institute, University of Wisconsin-Madison** |
| 2015		| Rising Star, **Association for Psychological Science** |
| 2014		| Intel Best Paper Award *This hand is my hand: A probabilistic approach to hand disambiguation in egocentric video*, **IEEE Computer Vision and Pattern Recognition** |
| 2013		| Postdoctoral Fellowship, NICHD Training Grant, 5T32HD7475-17, *Training Program in Integrative Developmental Process*, **Indiana University** |
| 2012		| Best Methodological Paper, *Understanding the development of motion processing by characterizing optic flow experienced by infants and their mothers*, **International Conference on Learning and Development** |
| 2011		| Martin Braine Dissertation Award, **New York University** |
| 2010		| Best Paper Award *Head-mounted eye-tracking of infants’ natural interactions:  A new method*, **ACM Eye Tracking Research & Applications** |
| 2009		| Sandra G. Wiener Student Investigator Award, **International Society for Developmental Psychobiology** |
: {tbl-colwidths="[5,95]"}

# Grant Support

### Extramural
 | 
|--|--------|
| 2022-2026 | James S. McDonnell Foundation Opportunity Award: [*Characterizing infants' everyday motor and object experiences through computer vision analysis of caregiver-captured video surveys.*](https://doi.org/10.37717/2022-3803) **John Franchak, PI, $250,000 4-year total.** |
| 2022-2026 | James S. McDonnell Foundation Opportunity Award: [*Sensorimotor cascades: Integrating real-time movement dynamics during the sleep and awake periods of human infants.*]() Drew Abney, PI, $250,000 4-year-total. **John Franchak, consultant.** |
| 2020-2024 | NSF BCS-1941449: [*Developmental cascades: How motor development alters everyday learning*](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1941449&HistoricalAwards=false). **John Franchak, PI, $754,957 4-year total.** |
| 2018-2023	| NICHD R01-HD-094830: *PLAY (Play and Learning Across a Year)*. Karen Adolph, PI, $6,341,419 total award. **John Franchak, sub-award PI, $18,527 5-year total.** |
| 2018-2022	| NSF IIS-1763966: *CHS: Medium: Collaborative research: Designing virtual worlds for children - A developmental study of how children act, perceive, and reason spatially*. Robert Bodenheimer, PI, $539,504 total award. **John Franchak, consultant, $24,000 4-year total.** |	
| 2018-2021	| NSF BCS-1749594: *Picture book reading: Investigating a key source of linguistic input for early language development*. Jessica Montag, PI, $427,933 3-year total. **John Franchak, consultant, $5000 3-year total.** |
| 2018-2023	| NICHD R01-HD-033486: *Flexibility of learning in infant skill acquisition*, Karen Adolph, PI, total award $3,086,397. **John Franchak, consultant, $25,000 5-year total.** |
: {tbl-colwidths="[15,85]"}

### Intramural
 | 
|--|--------|
| 2022-2023 | UCR Center for Health Disparities Research FIRST Pilot Grant: *Sociocultural and emotion regulation processes that contextualize health disparities in Latinx children's anxiety*. Elizabeth Davis, PI, $50,000 total award. **John Franchak, co-PI**. |
|2021-2022 | UCR Exploration Center for Innovative Teaching & Engagement: Remote Course Conversion Grant. **John Franchak, PI, $8,000 1-year total**. |
|2021-2022 | UCR Center for Health Disparities Research Interdisciplinary Research Working Group Award: *Contextualizing Latinx children’s developing psychopathology: An interdisciplinary investigation of sociocultural and psychological processes contributing to health disparities in anxiety*. Elizabeth Davis, PI $2,500 1-year total. **John Franchak, co-PI**. |
| 2019-2021	| UCR Regents Faculty Development Fellowship: *Characterizing everyday opportunities for learning in the second year of life*. **John Franchak, PI, $5,000 2-year total**. |
| 2015-2017	| UCR Regents Faculty Fellowship: *Developmental changes in visual experiences over the first year of life*. **John Franchak, PI, $6,000 2-year total**. |
: {tbl-colwidths="[15,85]"}

# Publications 
\renewcommand{\arraystretch}{1.5}

```{r}
#|output: false
#|echo: false
refs <- read_csv("publications/publications.csv") %>% 
  mutate(authors = str_replace(authors, "Franchak, J.M.", "**Franchak, J.M.**")) 
presentations <- read_csv("publications/presentations.csv") %>% 
  mutate(authors = str_replace(authors, "Franchak, J.M.", "**Franchak, J.M.**")) 
```
### Manuscripts Invited/Under Review/In Revision
```{r}
refs  %>%  
  filter(type %in% c("Prep")) %>% 
  mutate(citation = sprintf("%s (%s). %s", authors, year, title)) %>% 
  select(citation) %>% 
  kable(col.names = "") 
```

### Peer-Reviewed Publications
::: {.content-visible when-format="pdf"}
```{r}
refs %>% filter(type %in% c("Journal","Proceedings")) %>% 
  mutate(numbers = str_c(", ", numbers)) %>% 
  mutate(numbers = replace_na(numbers, "."),
         year = as.numeric(year)) %>% 
  mutate(citation = ifelse(inpress == 0,
                           sprintf("%d.  %s (%d). [%s](https://padlab.ucr.edu/publications/%s) *%s*%s", row_number(), authors, year, title, url, venue, numbers),
                           sprintf("%d.  %s (in press). [%s](https://padlab.ucr.edu/publications/%s) *%s*%s", row_number(), authors, title, url, venue, numbers))) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
refs %>% filter(type %in% c("Journal","Proceedings")) %>% 
  mutate(numbers = str_c(", ", numbers), year = as.numeric(year)) %>% 
  mutate(numbers = replace_na(numbers, ".")) %>% 
  mutate(citation = ifelse(inpress == 0,
                           sprintf("[{{< fa file-pdf >}}](https://padlab.ucr.edu/publications/%s)  %s (%d). %s *%s*%s", url, authors, year, title, venue, numbers),
                           sprintf("[{{< fa file-pdf >}}](https://padlab.ucr.edu/publications/%s)  %s (in press). %s *%s*%s", url, authors, title, venue, numbers))) %>% 
  select(citation) %>% kable(col.names = "")
```
:::

### Book Chapters
::: {.content-visible when-format="pdf"}
```{r}
refs %>% filter(type %in% c("Chapter")) %>% 
  mutate(numbers = str_c(", ", numbers)) %>% 
  mutate(numbers = replace_na(numbers, ""), year = as.numeric(year)) %>% 
  mutate(citation = ifelse(inpress == 0,
                           sprintf("%d.  %s (%d). [%s](https://padlab.ucr.edu/publications/%s) *%s*%s", row_number(), authors, year, title, url, venue, numbers),
                           sprintf("%d.  %s (in press). [%s](https://padlab.ucr.edu/publications/%s) *%s*%s", row_number(), authors, title, url, venue, numbers))) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
refs %>% filter(type %in% c("Chapter")) %>% 
  mutate(numbers = str_c(", ", numbers)) %>% 
  mutate(numbers = replace_na(numbers, ""), year = as.numeric(year)) %>% 
  mutate(citation = ifelse(inpress == 0,
                           sprintf("[{{< fa file-pdf >}}](https://padlab.ucr.edu/publications/%s) %s (%d). %s *%s*%s", url, authors, year, title, venue, numbers),
                           sprintf("[{{< fa file-pdf >}}](https://padlab.ucr.edu/publications/%s) %s (in press). %s *%s*%s", url, authors, title, venue, numbers))) %>% 
  select(citation) %>% kable(col.names = "")
```
:::

# Open Science 

### Shared Datasets
```{r}
read_csv("publications/datasets.csv") %>% arrange(desc(year)) %>% 
  mutate(citation = sprintf("(%d) *%s* %s. [```doi:%s```](%s)", year, title, venue, doi, paste0("https://doi.org/",doi))) %>% 
  select(citation) %>% kable(col.names = "")
```

### Open Source Research and Teaching Materials

- *Eye Tracking Accuracy Calculator*, [https://github.com/JohnFranchak/et_accuracy](https://github.com/JohnFranchak/et_accuracy)
- *Dynamic ROI Coder for Matlab*, [https://github.com/JohnFranchak/roi_coder](https://github.com/JohnFranchak/roi_coder)
- *Principles of Data Science Course*, [https://github.com/psych-259-data-science-2022](https://github.com/psych-259-data-science-2022)
- *ICIS Head-Mounted Eye Tracking Workshop*, [https://github.com/ICIS-HMET-Workshop](https://github.com/ICIS-HMET-Workshop)
- *Matlab Utilities for Eye Tracking*, [https://github.com/JohnFranchak/et_tools](https://github.com/JohnFranchak/et_tools)
- *Escalator Psychophysical Toolbox*, [https://github.com/JohnFranchak/escalator_toolbox](https://github.com/JohnFranchak/escalator_toolbox)

# Presentations
<!-- Should add some logic to sort these by date -->

### Conference Organizing
::: {.content-visible when-format="pdf"}
```{r}
presentations %>% filter(type %in% c("Organizing")) %>% 
  mutate(citation = sprintf("%d.  %s (%d, %s). *%s*. %s %s.", row_number(), authors, year, month, title, what, venue)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
presentations %>% filter(type %in% c("Organizing")) %>% 
  mutate(citation = sprintf("%s (%d, %s). *%s*. %s %s.", authors, year, month, title, what, venue)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::

### Conference Papers
::: {.content-visible when-format="pdf"}
```{r}
presentations %>% filter(type %in% c("Paper")) %>% arrange(desc(year)) %>% 
  mutate(citation = sprintf("%d.  %s (%d, %s). *%s*. %s %s.", row_number(), authors, year, month, title, what, venue)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
presentations %>% filter(type %in% c("Paper")) %>% arrange(desc(year)) %>% 
  mutate(citation = sprintf("%s (%d, %s). *%s*. %s %s.", authors, year, month, title, what, venue)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::

### Conference Posters
::: {.content-visible when-format="pdf"}
```{r}
presentations %>% filter(type %in% c("Poster")) %>% arrange(desc(year)) %>% 
  mutate(citation = sprintf("%d.  %s (%d, %s). *%s*. %s %s.", row_number(), authors, year, month, title, what, venue)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
presentations %>% filter(type %in% c("Poster")) %>% arrange(desc(year)) %>% 
  mutate(citation = sprintf("%s (%d, %s). *%s*. %s %s.", authors, year, month, title, what, venue)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::

### Invited Talks and Colloquia
\renewcommand{\arraystretch}{1.25}
::: {.content-visible when-format="pdf"}
```{r}
presentations %>% filter(type %in% c("Colloquium")) %>% arrange(desc(year)) %>% 
  mutate(citation = sprintf("%d. %s%s. (%d)", row_number(), ifelse(is.na(what), "", paste0(what, " ")), venue, year)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
::: {.content-visible when-format="html"}
```{r}
presentations %>% filter(type %in% c("Colloquium")) %>% arrange(desc(year)) %>% 
  mutate(citation = sprintf("(%d) %s%s.", year, ifelse(is.na(what), "", paste0(what, " ")), venue)) %>% 
  select(citation) %>% kable(col.names = "")
```
:::
\renewcommand{\arraystretch}{1.5}
# Media Coverage

| La Presse. (2018)  [*Les mystères des positions de bébés*](https://bit.ly/2Cqjya7)
| Science Daily. (2018) [*Study explores infant body position and learning*](https://www.sciencedaily.com/releases/2018/10/181023150036.htm) 
| Simon’s Foundation. (2011) [*Eye-tracking device travels with toddlers*](http://sfari.org/news-and-opinion/toolbox/2011/eye-tracking-device-travels-with-toddlers) 
| Voices of America, Science/Health News. (2010) [*New studies reveal infants’ world of vision*](http://www.voanews.com/english/news/health/New-Studies-Reveal-Infants-World-Of-Vision-104716684.html) 
| New York Times. (2010) [*Looking this way and that, and learning to adapt to the world*](http://www.nytimes.com/2010/08/17/science/17gaze.html) 

# Professional Activities and Service

### Reviewer Positions

\renewcommand{\arraystretch}{1.25}
| | |
|-|--------|
| 2024 | Member, National Eye Institute Grant Review Panel |
| 2024 | Area Chair, IEEE International Conference on Learning and Development |
| 2024 | Panel Reviewer, International Congress on Infant Studies | 
| 2024 | Panel Reviewer, Cognitive Development Society |
| 2022- | Associate Editor, *Developmental Psychology* | 
| 2022 | Member, National Science Foundation Review Panel |
| 2021 | Member, National Science Foundation Review Panel |
| 2020-2023 | Review Editor, Perception Science Editorial Board, *Frontiers in Psychology* and *Frontiers in Neuroscience* |
| 2022 | Panel Reviewer, International Congress on Infant Studies | 
| 2020 | Panel Reviewer, Society for Research in Child Development |
| 2020 | Scientific Committee, International Conference on Perception and Action (conference cancelled)|
| 2020 | Panel Reviewer, SRCD Special Topics Meeting on Learning Through Play and Imagination |
| 2020 | Panel Reviewer, International Congress on Infant Studies | 
| 2019 | Panel Reviewer, Cognitive Development Society |
| 2018 | Panel Reviewer, International Congress on Infant Studies |
| 2017 | Panel Reviewer, Society for Research in Child Development |
| 2016 | Panel Co-Chair, International Congress on Infant Studies | 
| 2016 | Panel Reviewer, SRCD Special Topics Meeting on Technology and Media in Children’s Development |
| 2015 | Scientific Committee, International Conference on Perception and Action|
: {tbl-colwidths="[15,85]"}

### Ad Hoc Reviewer

\renewcommand{\arraystretch}{1.25}
```{r}
adhoc <- read_csv("publications/adhoc.csv") %>% arrange(journal) %>% unlist()
col1 <- adhoc[1:ceiling(length(adhoc)/2)]
col2 <- adhoc[{ceiling(length(adhoc)/2)+1}:length(adhoc)]
if (length(col2) < length(col1)) {
  col2 <- c(col2, "")
}
tibble(col1, col2) %>% kable(col.names = c("",""))
```
\renewcommand{\arraystretch}{1.5}

### Professional Affiliations

| Division 7, American Psychological Association 
| Cognitive Development Society 
| International Congress on Infant Studies 
| International Society for Developmental Psychobiology 
| International Society for Ecological Psychology 
| Society for Research in Child Development  
| Vision Sciences Society 

# Teaching and Advising

### Courses Taught

| **Undergraduate:** 
| PSYC 12: Psychological Methods: Research Procedures (W15, F15, F16, F17, S19, S20, U20, F20, U21, F21, U22, S23, U23, F23) 
| PSYC 166A: Infancy (F19, S23, S24) 
| PSYC 169: Seminar: Perceptual-Motor Development (F14) 
| PSYC 169: Seminar: Infant Development (S17) 

| **Graduate:** 
| PSYC 207C: Processes of Cognitive Development (S16, S18, S21, S22, S24) 
| PSYC 258: Seminar: Vision in Everyday Behavior (S17) 
| PSYC 258: Seminar: Cascades in Development (W20) 
| PSYC 259: Principles of Data Science (W21, W22) 

### Student Advisees

| **Doctoral:**
| Zachary Kelly (current)
| Hailey Rousey (current)
| Yushan Guo (current)
| Chuan Luo (2023) 
| Kellan Kadooka (2022)  
| Brianna McGee (2022) 

| **Masters:**
| Jenna Monson (2018) 

| **Undergraduate Honors Theses:**
| Madelyn Caufield (2020) 
| Eli Labinger (2018)
| Frank Somoano (2017) 
| Angela Char (2011, as a postdoctoral mentor) 
| Emma Celano (2011, as a postdoctoral mentor) 
| Larissa Gabelman (2009, as a graduate mentor) 
| Dina van der Zalm (2008, as a graduate mentor) 

| **Undergraduate Research Grants Mentored:**
| Juelle Ford (2022), UCR Student Minigrant
| Faizah Ahmed (2022), UCR Student Minigrant
| Vivian Huynh (2022), UCR Student Minigrant
| Jino Sirivatanarat (2022), UCR Student Minigrant
| Gabrielle Blanch (2019), UCR Student Travel Grant 
| Madelyn Caufield (2019), UCR Student Minigrant 
| Yee Lat (2019), UCR Student Minigrant 
| Kelsey Michaels (2019), UCR Student Minigrant
| Gabrielle Blanch (2018), UCR Student Minigrant
| Tramanh Truong (2018), UCR Student Minigrant 
| Eli Labinger (2017), Chancellor’s Distinguished Fellowship 

# University Service

\renewcommand{\arraystretch}{1.25}
| | |
|-|--------|
| 2023- | Member, UCR Senate Committee on Information Technology |
| 2023- | Member, UCR Institutional Review Board |
| 2023- | Chair, UCR Psychology Developmental Area |
| 2023 | Faculty mentor, UCR Graduate Student Mentorship Program |
| 2023 | Member, Faculty Search Committee (Dept. of Psychology) | 
| 2023 | Member, UCR Chancellor's Distinguished Fellowship Advisory Board |
| 2023 | Member, UCR Undergraduate Research & Creative Activities Symposium Faculty Advisory Board |
| 2022 | Member, UCR Psychology ad hoc Instructional Technology Committee |
| 2019-2023 | Member, UC Riverside Academic Integrity Committee |
| 2019- | Psychology Department Colloquium Series Organizer |
| 2018 | Judge, Undergraduate Research Symposium |
| 2017-2023 | Member, Undergraduate Minigrant Review Committee |
| 2017 | R'Course Facilitator |
| 2016-2017 | Member, Graduate Admissions Committee (Dept. of Psychology) |
| 2015- | Chair, Child Studies @ UCR, [childstudies.ucr.edu](https://childstudies.ucr.edu)|
| 2014-2015 | Member, Faculty Search Committee (Dept. of Psychology) |
: {tbl-colwidths="[15,85]"}
